Making Sequential Programs Deterministic

### 2019-03-28 design.tex
Initial edits in section 2.3

\TheDeterminismChecker supports three types of polymorphism:  type
polymorphism, basetype polymorphism, and qualifier polymorphism.
Type polymorphism is handled by Java's generics mechanism, which
\theDeterminismChecker fully supports, including class and method generics,
inference, etc.
Basetype polymorphism is enabled by writing a type qualifier on a use of a
type variable.
Java does not provide a syntax that can be used for qualifier polymorphism,
so we use a special type qualifier name, \<@PolyDet>.
A method \<m> with signature $\forall \kappa . \kappa \<int> \times \<Det boolean> \rightarrow
\kappa \<String>$ would be written in our dialect of Java as
\begin{Verbatim}
@PolyDet String m(@PolyDet int, @Det boolean)
\end{Verbatim}

Each use of \<@PolyDet> stands for a use of the qualifier variable
$\kappa$, and there is no need to declare the qualifier variable $\kappa$.

>>>>

Our type system supports three types of polymorphism:  type
polymorphism, basetype polymorphism, and qualifier polymorphism.
\todo{Give an example for each.}
\begin{itemize}
\item
In \theDeterminismCheckerimplementation,
Type polymorphism is handled by Java's generics mechanism, which
\theDeterminismChecker fully supports, including class and method generics,
inference, etc.
\item
Basetype polymorphism is enabled by writing a type qualifier on a use of a
type variable.
\item
Java does not provide a syntax that can be used for qualifier polymorphism,
so we use a special type qualifier name, \<@PolyDet>.
A qualifier-polymorphic method \<m> with signature $\forall \kappa . \kappa \<int> \times \<Det boolean> \rightarrow
\kappa \<String>$ would be written in our dialect of Java as
\begin{Verbatim}
@PolyDet String m(@PolyDet int, @Det boolean)
\end{Verbatim}
Each use of \<@PolyDet> stands for a use of the qualifier variable
$\kappa$, and there is no need to declare the qualifier variable $\kappa$.
\TheDeterminismChecker currently supports
qualifier
polymorphism on methods but not on classes.
Therefore, \<@PolyDet> may be written in methods (signatures and bodies)
but not on fields.
\end{itemize}
